---
title: "Online Job Vacancies Web scraped from National Employment Agency Romania (RO)"
subtitle: "Q1 2020"
author: "INS-RO"
date: "9/20/2020"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(knitr)
library(ggplot2)
myfile <- "anofm_2020-03-28.csv"
my_col_types <- "ccDcccccccccdccTTcdddccccccccccccccccccccccTc"
ojv_anofm <- read_csv(myfile, col_types = my_col_types, n_max = 5)
ojv_anofm_names <- names(ojv_anofm)
ojv_anofm <- read_csv(myfile, col_names = FALSE, col_types = paste0(rep("c", 45), collapse = ""), skip = 1)
names(ojv_anofm) <- ojv_anofm_names
source("utils.R")
```

# Potential indicators from OJVs collected from National Employment Agency - Romania

## Potential indicators from OJVs - Methodological framework V1

* Number of available on-line job vacancies in a reference day  
* Number of OJAs web scraped in a reference day by COR/ESCO level 2  
* Number of OJVs web scraped in a reference day by required educational level    
* Number of OJAs web scraped in a reference day by CAEN/NACE  
* Number of OJAs web scraped in a reference day by Working Time  
* Number of OJAs web scraped in a reference day by Experience Years  
* Number of OJAs web scraped in a reference day by County  
* Number of OJAs web scraped in a reference day by Region Code  
* Daily pseudo-stocks of job ads based on CEDEFOP data  


# Results for Potential indicators from OJVs  

## Dates and times of observations

```{r echo=FALSE, message=FALSE, warning=FALSE}
ojv_anofm %>% 
  distinct(POSTED_JOBS_ID, .keep_all = TRUE) %>%
  select(EXPIRATION_DATE) %>% 
  unlist() %>%
  as.vector() %>%
  as.Date.character(origin = "1970-01-01") -> tmp1
  tmp1 <- tmp1[tmp1 < as.Date("2025-01-01")]
  tmp1 <- range(tmp1)
  minDate <- tmp1[1]
  maxDate <- tmp1[2]
  rm(tmp1)
```

The interval in which the OJVs are available (not expirated):  `r paste0(minDate, " - ", maxDate)`.  


## Number of available on-line job vacancies in a reference day  

Data collected from National Employment Agency from Romania refers to all observations webscraped in the reference day of JVS from website www.anofm.ro, the last day of the second month of a quarter (March 2020).    
In the National Employment Agency database there are `r nrow(ojv_anofm)` observations in the reference day.  
Of these, the total number of unique OJV is `r nrow(ojv_anofm %>% select(POSTED_JOBS_ID) %>% distinct())`.  
The total number of JVs posted in the National Employment Agency is `r format(as.numeric(ojv_anofm %>% select(NR_LMV) %>% summarise(TOTAL_NR_LMV = sum(as.numeric(NR_LMV)))), scientific = FALSE)`.  
The number of employers who posted the OJV is `r nrow(ojv_anofm %>% select(CF) %>% distinct())`.  


## Number of OJAs web scraped in a reference day by COR level 2  

```{r echo=FALSE, message=FALSE, warning=FALSE}
ojv_anofm %>% 
  distinct(POSTED_JOBS_ID, .keep_all = TRUE) %>%
  select(COR_CODE, NR_LMV) %>%
  mutate(COR_CODE_2c = stringr::str_sub(COR_CODE, 1, 2)) %>%
  group_by(COR_CODE_2c) %>%
  summarise(Freq = sum(as.numeric(NR_LMV))) -> ojv_anofm_cor
names(ojv_anofm_cor) <- c("COR_level_2", "Freq")
g1 <- ggplot(ojv_anofm_cor, aes(x = COR_level_2, y = Freq)) +
  geom_bar(stat = "identity", width=0.7, fill="steelblue") + 
  ggtitle("COR Level 2") +
  labs(x = 'COR', y = 'Number of vacancies') + 
  theme_minimal() +
  theme(axis.text.x = element_text(size=7, angle = 90, hjust = 1, vjust = 0))
print(g1)
```

## Number of OJVs web scraped in a reference day by required educational level

```{r echo=FALSE, message=FALSE, warning=FALSE}
isced <- read.csv("SCHOOL_TYPE_ISCED.csv")
ojv_anofm <- merge(ojv_anofm, isced, by = c("SCHOOL_TYPE"), all.x = TRUE)
rm(isced)
ojv_anofm %>% 
  distinct(POSTED_JOBS_ID, .keep_all = TRUE) %>%
  select(ISCED, NR_LMV) %>%
  group_by(ISCED) %>%
  summarise(Freq = sum(as.numeric(NR_LMV))) -> ojv_anofm_ed_lev
names(ojv_anofm_ed_lev) <- c("Educational_level", "Freq")
g1 <- ggplot(ojv_anofm_ed_lev, aes(x = Educational_level, y = Freq)) +
  geom_bar(stat = "identity", width=0.7, fill="steelblue") + 
  ggtitle("Number of OJVs web scraped by Educational level") +
  labs(x = 'Educational level', y = 'Number of vacancies') + 
  theme_minimal() +
  theme(axis.text.x = element_text(size=7, angle = 90, hjust = 1, vjust = 0))
print(g1)
```

## Number of OJAs web scraped in a reference day by CAEN  

```{r echo=FALSE, message=FALSE, warning=FALSE}
ojv_anofm %>% 
  distinct(POSTED_JOBS_ID, .keep_all = TRUE) %>%
  select(COD_CAEN, NR_LMV) %>%
  mutate(COD_CAEN = stringr::str_sub(COD_CAEN, 1, 2)) %>%
  group_by(COD_CAEN) %>%
  summarise(Freq = sum(as.numeric(NR_LMV))) -> ojv_anofm_caen
names(ojv_anofm_caen) <- c("COD_CAEN", "Freq")
g1 <- ggplot(ojv_anofm_caen, aes(x = COD_CAEN, y = Freq)) +
  geom_bar(stat = "identity", width=0.7, fill="steelblue") + 
  ggtitle("COD CAEN") +
  labs(x = 'COD_CAEN', y = 'Number of vacancies') + 
  theme_minimal() +
  theme(axis.text.x = element_text(size=7, angle = 90, hjust = 1, vjust = 0))
print(g1)
```

## Number of OJAs web scraped in a reference day by Working Time  

```{r echo=FALSE, message=FALSE, warning=FALSE}
ojv_anofm %>% 
  distinct(POSTED_JOBS_ID, .keep_all = TRUE) %>%
  select(WORKING_TIME, NR_LMV) %>%
  group_by(WORKING_TIME) %>%
  summarise(Freq = sum(as.numeric(NR_LMV))) -> ojv_anofm_wt
names(ojv_anofm_wt) <- c("WORKING_TIME", "Freq")
g1 <- ggplot(ojv_anofm_wt, aes(x = WORKING_TIME, y = Freq)) +
  geom_bar(stat = "identity", width=0.7, fill="steelblue") + 
  ggtitle("WORKING TIME") +
  labs(x = 'Working Time', y = 'Number of vacancies') + 
  theme_minimal() +
  theme(axis.text.x = element_text(size=9, hjust = 1, vjust = 0))
print(g1)
```

## Number of OJAs web scraped in a reference day by Experience Years  

```{r echo=FALSE, message=FALSE, warning=FALSE}
exp_years <- read.csv("exp_years.csv")
ojv_anofm <- merge(ojv_anofm, exp_years, by = c("experienta"), all.x = TRUE)
rm(exp_years)
ojv_anofm %>% 
  distinct(POSTED_JOBS_ID, .keep_all = TRUE) %>%
  select(exp_years, NR_LMV) %>%
  group_by(exp_years) %>%
  summarise(Freq = sum(as.numeric(NR_LMV))) -> ojv_anofm_ey
names(ojv_anofm_ey) <- c("exp_years", "Freq")
g1 <- ggplot(ojv_anofm_ey, aes(x = exp_years, y = Freq)) +
  geom_bar(stat = "identity", width=0.7, fill="steelblue") + 
  ggtitle("Experience Years") +
  labs(x = 'Experience Years', y = 'Number of vacancies') + 
  theme_minimal() +
  theme(axis.text.x = element_text(size=9, hjust = 1, vjust = 0))
print(g1)
```


## Number of OJAs web scraped in a reference day by County  

```{r echo=FALSE, message=FALSE, warning=FALSE}
ojv_anofm %>% 
  distinct(POSTED_JOBS_ID, .keep_all = TRUE) %>%
  select(ABBR, NR_LMV) %>%
  group_by(ABBR) %>%
  summarise(Freq = sum(as.numeric(NR_LMV))) -> ojv_anofm_jud
names(ojv_anofm_jud) <- c("ABBR", "Freq")
g1 <- ggplot(ojv_anofm_jud, aes(x = ABBR, y = Freq)) +
  geom_bar(stat = "identity", width=0.7, fill="steelblue") + 
  ggtitle("County") +
  labs(x = 'County Code', y = 'Number of vacancies') + 
  theme_minimal() +
  theme(axis.text.x = element_text(size=7, angle = 90, hjust = 1, vjust = 0))
print(g1)
```


## Number of OJAs web scraped in a reference day by Region Code  

```{r echo=FALSE, message=FALSE, warning=FALSE}
ojv_anofm %>% 
  distinct(POSTED_JOBS_ID, .keep_all = TRUE) %>%
  select(REGION_CODE, NR_LMV) %>%
  group_by(REGION_CODE) %>%
  summarise(Freq = sum(as.numeric(NR_LMV))) -> ojv_anofm_rc
names(ojv_anofm_rc) <- c("REGION_CODE", "Freq")
g1 <- ggplot(ojv_anofm_rc, aes(x = REGION_CODE, y = Freq)) +
  geom_bar(stat = "identity", width=0.7, fill="steelblue") + 
  ggtitle("REGION CODE") +
  labs(x = 'Region Code', y = 'Number of vacancies') + 
  theme_minimal() +
  theme(axis.text.x = element_text(size=7, angle = 90, hjust = 1, vjust = 0))
print(g1)
```

## Number of OJAs web scraped in a reference day by Organization   

```{r echo=FALSE, message=FALSE, warning=FALSE}
ojv_anofm %>% 
  distinct(POSTED_JOBS_ID, .keep_all = TRUE) %>%
  select(ORGANIZATION_ID, NR_LMV) %>%
  group_by(ORGANIZATION_ID) %>%
  summarise(Freq = sum(as.numeric(NR_LMV))) -> ojv_anofm_org
names(ojv_anofm_org) <- c("ORGANIZATION_ID", "Freq")
ojv_anofm_org %>%
  select(NR_LMV = Freq) %>%
  group_by(NR_LMV) %>%
  summarise(Freq = n()) -> ojv_anofm_org
g1 <- ggplot(ojv_anofm_org, aes(x = NR_LMV, y = Freq)) +
  geom_bar(stat = "identity", width=0.7, fill="steelblue") + 
  ggtitle("No of Organizations per No JVs") +
  labs(x = 'No of JVs', y = 'Number of organizations') + 
  theme_minimal() +
  theme(axis.text.x = element_text(size=7, angle = 90, hjust = 1, vjust = 0))
print(g1)
```

